Joint training of classification model and similarity model for low-resource text classification in chatbot

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
modified:   paper.tex   new file:   picture/improvement_trend.jpg

  \subsubsection*{How does training sample size influence SFC?} 
  We analyze the
  overall  improvement  trend  of  SFC under various few-shot settings.

  Our main
  focus  is  to  study  chatbot  building  in common situation during real-world
  application  where  only  a few sample sentences are available for each class.
  The  experimental  results  for  the  3  diverse  intention detection datasets
  (ClINC150,  BANKING77,  HWU64)  under  few-shot  settings, 5 to 20 samples per
  class,  indicate that our proposed joint SFC can achieve 2.47 percents average
  improvement   over  one  of  the  most  powerful  baseline  models,  which  is
  RoBERTa-large  classification  model.  Moreover,  the  improvement  in F1 score
  becomes  more  and  more prominent with the decrease of data sample number per
  class.

>>>>

  \subsubsection*{How does training sample size influence SFC?} 
  We analyze the overall  improvement  trend  of  SFC under various few-shot
  settings, and show results in Fig. \ref{fig:trend}.

  Our main focus  is  to  study  chatbot  building  in common situation during real-world
  application  where  only  a few sample sentences are available for each class.
  The  experimental  results  for  the  3  diverse  intention detection datasets
  (ClINC150,  BANKING77,  HWU64)  under  few-shot  settings, 5 to 50 samples per
  class,  indicate that our proposed joint SFC can achieve 2.47 percents average
  improvement   over  one  of  the  most  powerful  baseline  models,  which  is
  RoBERTa-large  classification  model.  Moreover,  the  improvement  in F1 score
  becomes  more  and  more prominent with the decrease of data sample number per
  class.

  \begin{figure}[t]
    \begin{centering}
      \includegraphics[scale=0.2]{picture/improvement_trend.jpg} 
      \par
    \end{centering}
    \caption{
      Improvements with different size of training data.
    }
    \label{fig:trend}
  \end{figure}
